SOC budget analysis in comparsion to LPJmL4 ad SoilGrids 2.0

### 2022-07-20 ResultNotebooks/results_SOCpointvalidate.Rmd
update of output scripts and figure

---
title: "SOC budget analysis in comparsion"
output:
  html_document:
    df_print: paged
  pdf_document: default
  bookdown::pdf_document2: default
   keep_md: true
---

@@

SoilCarbon <- readRDS(paste0("Data/", rev, scen, "/SoilCarbon.rds"))
Landuse    <- readRDS(paste0("Data/", rev, scen, "/Landuse.rds"))

```

@@

  for(u in unique) {
    sand_reduced[u, , "natveg.mean"]   <- mean(    as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==1])
    sand_reduced[u, , "crop.mean"]     <- mean(    as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==0])
    sand_reduced[u, , "natveg.median"] <- median(  as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==1])
    sand_reduced[u, , "crop.median"]   <- median(  as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==0])
    sand_reduced[u, , "natveg.max"]    <- max(     as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==1])
    sand_reduced[u, , "crop.max"]      <- max(     as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==0])
    sand_reduced[u, , "natveg.min"]    <- min(     as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==1])
    sand_reduced[u, , "crop.min"]      <- min(     as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==0])
    sand_reduced[u, , "natveg.q25"]    <- quantile(as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==1], probs = 0.25)
    sand_reduced[u, , "crop.q25"]      <- quantile(as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==0], probs = 0.25)
    sand_reduced[u, , "natveg.q75"]    <- quantile(as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==1], probs = 0.75)
    sand_reduced[u, , "crop.q75"]      <- quantile(as.array(sand[u, ,"SOC"])[sand[u,,"Native"]==0], probs = 0.75)
  }

@@

  sand_natveg_table <- reshape2::dcast(as.data.frame(sand_reduced[, , "natveg"]), 
                                        Region ~ Data2, value.var = "Value")
  sand_natveg_table$Cell   <- gsub("_", "\\.", sand_natveg_table$Region)
  sand_natveg_table$Native <- 1
  sand_natveg_table        <- sand_natveg_table[complete.cases(sand_natveg_table), ][-1]

```

@@

correlations[, , "median.natveg"] <- cor.test(statsPoints$median[statsPoints$Native == 1], statsPoints$thisStudy[statsPoints$Native == 1])$estimate^2
correlations[, , "mean.natveg"]   <- cor.test(statsPoints$mean[  statsPoints$Native == 1], statsPoints$thisStudy[statsPoints$Native == 1])$estimate^2
correlations[, , "median.crop"]   <- cor.test(statsPoints$median[statsPoints$Native == 0], statsPoints$thisStudy[statsPoints$Native == 0])$estimate^2
correlations[, , "mean.crop"]     <- cor.test(statsPoints$mean[  statsPoints$Native == 0], statsPoints$thisStudy[statsPoints$Native == 0])$estimate^2

correlations[, , "allP.allLU"]    <- cor.test(allPoints$ValidationData, allPoints$thisStudy)$estimate^2
correlations[, , "allP.natveg"]   <- cor.test(allPoints$ValidationData[allPoints$Native == 0], allPoints$thisStudy[allPoints$Native == 0])$estimate^2
correlations[, , "allP.crop"]     <- cor.test(allPoints$ValidationData[allPoints$Native == 1], allPoints$thisStudy[allPoints$Native == 1])$estimate^2

```

@@

SOCPointValid  <- ggplot() + 
                  geom_point(data = statsPoints, 
                            aes(alpha = str_wrap("Median (R2=0.13)", 7), x = median, y = thisStudy, colour = factor(Native)),
                            shape = 3, size = 2) +
                  geom_segment(data = statsPoints,
                               aes(alpha = "Min-Max", x = min, y = thisStudy, xend = max, yend = thisStudy, 
                                   colour = factor(Native)), 
                               size = 0.5) +
                  geom_point(data = allPoints, 
                             aes(alpha = "Point Data", x = ValidationData, y = thisStudy, colour = factor(Native)),
                             shape = 1, size = 0.5) +
                  labs( x = "Point measurement data (tC/ha) ", y = "Predicted value by this study (tC/ha)") +
                  scale_x_continuous(trans = 'log10', limits = c(7, 470)) + 
                  scale_y_continuous(trans = 'log10', limits = c(7, 470)) +
                  coord_fixed(1) + theme(aspect.ratio=1) +
                  geom_abline(slope=1, intercept=0, color = "grey", size = 0.5, linetype = "dashed") + 
                  theme(rect=element_blank(),
                        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
                        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
                        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
                        axis.text.y = element_text(size = legend_size),
                        legend.position= c(0.87, 0.2), legend.direction="vertical",
                        legend.title = element_text(size = legend_size), 
                        legend.text  = element_text(size = legend_size),
                        legend.spacing.y = unit(0.1, "cm")) +
                  scale_color_manual(values = scen_cols, labels = c("Cropland", str_wrap("Natural vegetation", 7)), name = "") +
                  scale_alpha_manual(name = NULL,
                                     values = c(1, 1, 1),
                                     breaks = c(str_wrap("Median (R2=0.13)", 7), "Min-Max", "Point Data"),
                                     guide = guide_legend(override.aes = list(linetype = c(0, 1, 0),
                                                                                 shape = c(3, NA, 1),
                                                                                  size = c(2, 0.5, 0.5), 
                                                                                 color = "black")))

@@

ggsave(paste0(outputdir,"scatterComparePointData_2010.png"), plot=SOCPointValid, height=16, width=16, units="cm", dpi = 300)

```

@@

p <- ggplot(testcrop, aes(x=Value, y=soc)) + geom_boxplot() + coord_flip()

@@

  points(sand[,,"soc"][sand[,,"native"] == 0],SOCStock_crop_raw[getCells(sand),year,][sand[,,"native"] == 0], col ="red")
  lines(c(-1000, 1000), c(-1000, 1000), col = "grey")

@@

  plot(sand_reduced[,,"soc_nat"][                        !is.na(sand_reduced[,,"soc_nat"])],
       SOCStock_natveg_raw[getCells(sand_reduced),year,][!is.na(sand_reduced[,,"soc_nat"])], 
       xlab = "Sandermann", ylab = "This Study",
       xlim = c(0, unname(lim)), ylim = c(0, unname(lim)))

  points(sand_reduced[,,"soc_crop"][                     !is.na(sand_reduced[,,"soc_crop"])],
         SOCStock_crop_raw[getCells(sand_reduced),year,][!is.na(sand_reduced[,,"soc_crop"])], 
         col ="red")
  lines(c(-1000, 1000), c(-1000, 1000), col = "grey")

@@

    lines(c(sand_reduced[u,,"soc_crop"] - sand_reduced[u,,"sd_crop"], 
            sand_reduced[u,,"soc_crop"] + sand_reduced[u,,"sd_crop"]), 
          c(SOCStock_crop_raw[u,year,],
            SOCStock_crop_raw[u,year,]), col = "pink")

    lines(c(sand_reduced[u,,"soc_nat"] - sand_reduced[u,,"sd_nat"], 
            sand_reduced[u,,"soc_nat"] + sand_reduced[u,,"sd_nat"]), 
          c(SOCStock_natveg_raw[u,year,],
            SOCStock_natveg_raw[u,year,]), col = "grey")

  }

```

@@

  y <- c(SOCStock_crop_raw[    getCells(sand), year, ][sand[, , "native"] == 0], 
         SOCStock_natveg_raw[getCells(sand), year, ][sand[, , "native"] == 1])#

  x_clean <- c(sand[, , "soc"][sand[, , "native"] == 0],
               sand[, , "soc"]["CHN.9964",,,invert=TRUE][sand[, , "native"] == 1])

  y_clean <- c(SOCStock_crop_raw[  getCells(sand), year, ][sand[, , "native"] == 0], 
               SOCStock_natveg_raw[getCells(sand), year, ]["CHN.9964",,,invert=TRUE][sand[, , "native"] == 1])

@@

  x_red  <- c(sand_reduced[, , "soc_nat" ][!is.na(sand_reduced[, , "soc_nat" ])],
              sand_reduced[, , "soc_crop"][!is.na(sand_reduced[, , "soc_crop"])])

  y_red  <- c(SOCStock_natveg_raw[getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_nat" ])],
              SOCStock_crop_raw[  getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_crop"])])

  x_red2  <- c(sand_reduced[, , "soc_nat" ]["CHN.9964",,,invert=TRUE][!is.na(sand_reduced[, , "soc_nat" ])],
              sand_reduced[, , "soc_crop"][!is.na(sand_reduced[, , "soc_crop"])])

  y_red2  <- c(SOCStock_natveg_raw[getCells(sand_reduced), year, ]["CHN.9964",,,invert=TRUE][!is.na(sand_reduced[, , "soc_nat" ])],
              SOCStock_crop_raw[  getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_crop"])])

  cor(x, y)^2
  cor.test(x, y)$estimate^2
  cor.test(x_clean, y_clean)$estimate^2
  cor.test(x_crop, y_crop)$estimate^2
  cor.test(x_red, y_red)$estimate^2
  cor.test(log(x_red2), log(y_red2))$estimate^2

```

>>>>

---
title: "SOC budget analysis in comparsionto point-based measurements"
output:
  html_document:
    df_print: paged
  pdf_document: default
  bookdown::pdf_document2: default
   keep_md: true
---

@@

SoilCarbon <- readRDS(paste0("Data/", rev, scen, "/SoilCarbon.rds"))
Landuse    <- readRDS(paste0("Data/", rev, scen, "/Landuse.rds"))
```

@@

  for (u in unique) {
    sand_reduced[u, , "natveg.mean"]   <- mean(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 1])
    sand_reduced[u, , "crop.mean"]     <- mean(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 0])
    sand_reduced[u, , "natveg.median"] <- median(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 1])
    sand_reduced[u, , "crop.median"]   <- median(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 0])
    sand_reduced[u, , "natveg.max"]    <- max(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 1])
    sand_reduced[u, , "crop.max"]      <- max(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 0])
    sand_reduced[u, , "natveg.min"]    <- min(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 1])
    sand_reduced[u, , "crop.min"]      <- min(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 0])
    sand_reduced[u, , "natveg.q25"]    <- quantile(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 1], probs = 0.25)
    sand_reduced[u, , "crop.q25"]      <- quantile(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 0], probs = 0.25)
    sand_reduced[u, , "natveg.q75"]    <- quantile(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 1], probs = 0.75)
    sand_reduced[u, , "crop.q75"]      <- quantile(as.array(sand[u, , "SOC"])[sand[u, , "Native"] == 0], probs = 0.75)
  }

@@

  sand_natveg_table <- reshape2::dcast(as.data.frame(sand_reduced[, , "natveg"]),
                                        Region ~ Data2, value.var = "Value")
  sand_natveg_table$Cell   <- gsub("_", "\\.", sand_natveg_table$Region)
  sand_natveg_table$Native <- 1
  sand_natveg_table        <- sand_natveg_table[complete.cases(sand_natveg_table), ][-1]
```

@@

correlations[, , "median.natveg"] <- cor.test(statsPoints$median[statsPoints$Native == 1], statsPoints$thisStudy[statsPoints$Native == 1])$estimate^2
correlations[, , "mean.natveg"]   <- cor.test(statsPoints$mean[statsPoints$Native == 1], statsPoints$thisStudy[statsPoints$Native == 1])$estimate^2
correlations[, , "median.crop"]   <- cor.test(statsPoints$median[statsPoints$Native == 0], statsPoints$thisStudy[statsPoints$Native == 0])$estimate^2
correlations[, , "mean.crop"]     <- cor.test(statsPoints$mean[statsPoints$Native == 0], statsPoints$thisStudy[statsPoints$Native == 0])$estimate^2

correlations[, , "allP.allLU"]    <- cor.test(allPoints$ValidationData, allPoints$thisStudy)$estimate^2
correlations[, , "allP.natveg"]   <- cor.test(allPoints$ValidationData[allPoints$Native == 0], allPoints$thisStudy[allPoints$Native == 0])$estimate^2
correlations[, , "allP.crop"]     <- cor.test(allPoints$ValidationData[allPoints$Native == 1], allPoints$thisStudy[allPoints$Native == 1])$estimate^2
```

@@

SOCPointValid  <- ggplot() +
                  geom_point(data = statsPoints,
                            aes(alpha = str_wrap("Median (R2=0.13)", 7),
                                x = median, y = thisStudy, colour = factor(Native)),
                            shape = 3, size = 2) +
                  geom_segment(data = statsPoints,
                               aes(alpha = "Min-Max",
                                   x = min, y = thisStudy, xend = max, yend = thisStudy,
                                   colour = factor(Native)),
                               size = 0.5) +
                  geom_point(data = allPoints,
                             aes(alpha = "Point Data",
                                 x = ValidationData, y = thisStudy, colour = factor(Native)),
                             shape = 1, size = 0.5) +
                  labs(x = "Point measurement data (tC/ha) ", y = "Predicted value by this study (tC/ha)") +
                  scale_x_continuous(trans = "log10", limits = c(7, 470)) +
                  scale_y_continuous(trans = "log10", limits = c(7, 470)) +
                  coord_fixed(1) + theme(aspect.ratio = 1) +
                  geom_abline(slope = 1, intercept = 0, color = "grey", size = 0.5, linetype = "dashed") +
                  theme(rect = element_blank(),
                        axis.title.y = element_text(size = legend_size,
                                                   margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
                        axis.title.x = element_text(size = legend_size,
                                                   margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
                        axis.text.x = element_text(angle = 60, hjust = 0.8, vjust = 0.8, size = legend_size),
                        axis.text.y = element_text(size = legend_size),
                        legend.position = c(0.87, 0.2), legend.direction = "vertical",
                        legend.title = element_text(size = legend_size),
                        legend.text  = element_text(size = legend_size),
                        legend.spacing.y = unit(0.1, "cm")) +
                  scale_color_manual(values = scen_cols,
                                     labels = c("Cropland", str_wrap("Natural vegetation", 7)), name = "") +
                  scale_alpha_manual(name = NULL,
                                     values = c(1, 1, 1),
                                     breaks = c(str_wrap("Median (R2=0.13)", 7), "Min-Max", "Point Data"),
                                     guide = guide_legend(override.aes = list(linetype = c(0, 1, 0),
                                                                                 shape = c(3, NA, 1),
                                                                                  size = c(2, 0.5, 0.5),
                                                                                 color = "black")))

@@

ggsave(paste0(outputdir, "scatterComparePointData_2010.png"), 
       plot = SOCPointValid, height = 16, width = 16, units = "cm", dpi = 300)
```

@@

p <- ggplot(testcrop, aes(x = Value, y = soc)) + geom_boxplot() + coord_flip()

@@

  points(sand[, , "soc"][sand[, , "native"] == 0], SOCStock_crop_raw[getCells(sand), year, ][sand[, , "native"] == 0], col = "red")
  lines(c(-1000, 1000), c(-1000, 1000), col = "grey")

@@

  plot(sand_reduced[, , "soc_nat"][!is.na(sand_reduced[, , "soc_nat"])],
       SOCStock_natveg_raw[getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_nat"])],
       xlab = "Sandermann", ylab = "This Study",
       xlim = c(0, unname(lim)), ylim = c(0, unname(lim)))

  points(sand_reduced[, , "soc_crop"][!is.na(sand_reduced[, , "soc_crop"])],
         SOCStock_crop_raw[getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_crop"])],
         col = "red")
  lines(c(-1000, 1000), c(-1000, 1000), col = "grey")

@@

    lines(c(sand_reduced[u, , "soc_crop"] - sand_reduced[u, , "sd_crop"],
            sand_reduced[u, , "soc_crop"] + sand_reduced[u, , "sd_crop"]),
          c(SOCStock_crop_raw[u, year, ],
            SOCStock_crop_raw[u, year, ]), col = "pink")

    lines(c(sand_reduced[u, , "soc_nat"] - sand_reduced[u, , "sd_nat"],
            sand_reduced[u, , "soc_nat"] + sand_reduced[u, , "sd_nat"]),
          c(SOCStock_natveg_raw[u, year, ],
            SOCStock_natveg_raw[u, year, ]), col = "grey")

  }
```

@@

  y <- c(SOCStock_crop_raw[getCells(sand), year, ][sand[, , "native"] == 0],
         SOCStock_natveg_raw[getCells(sand), year, ][sand[, , "native"] == 1]) #

  x_clean <- c(sand[, , "soc"][sand[, , "native"] == 0],
               sand[, , "soc"]["CHN.9964", , , invert = TRUE][sand[, , "native"] == 1])

  y_clean <- c(SOCStock_crop_raw[getCells(sand), year, ][sand[, , "native"] == 0],
               SOCStock_natveg_raw[getCells(sand), year, ]["CHN.9964", , , invert = TRUE][sand[, , "native"] == 1])

@@

  x_red  <- c(sand_reduced[, , "soc_nat"][!is.na(sand_reduced[, , "soc_nat"])],
              sand_reduced[, , "soc_crop"][!is.na(sand_reduced[, , "soc_crop"])])

  y_red  <- c(SOCStock_natveg_raw[getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_nat"])],
              SOCStock_crop_raw[getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_crop"])])

  x_red2  <- c(sand_reduced[, , "soc_nat"]["CHN.9964", , , invert = TRUE][!is.na(sand_reduced[, , "soc_nat"])],
              sand_reduced[, , "soc_crop"][!is.na(sand_reduced[, , "soc_crop"])])

  y_red2  <- c(SOCStock_natveg_raw[getCells(sand_reduced), year, ]["CHN.9964", , , invert = TRUE][!is.na(sand_reduced[, , "soc_nat"])],
              SOCStock_crop_raw[getCells(sand_reduced), year, ][!is.na(sand_reduced[, , "soc_crop"])])

  cor(x, y)^2
  cor.test(x, y)$estimate^2
  cor.test(x_clean, y_clean)$estimate^2
  cor.test(x_crop, y_crop)$estimate^2
  cor.test(x_red, y_red)$estimate^2
  cor.test(log(x_red2), log(y_red2))$estimate^2
```

### 2022-07-20 ResultNotebooks/results_SOCscattervalidate.Rmd
update of output scripts and figure

---
title: "SOC budget analysis in comparsion"
output:
  html_document:
    df_print: paged
  pdf_document: default
  bookdown::pdf_document2: default
   keep_md: true
---

@@

SoilCarbon <- readRDS(paste0("Data/", rev, "histManagement/SoilCarbon.rds"))
Landuse    <- readRDS(paste0("Data/", rev, "histManagement/Landuse.rds"))

```

@@

cropland        <- Landuse[,,"crop"]
SOCStock_natveg <- dimSums(SoilCarbon[,,c("naturalstate.natveg")], dim=3)
SOCStock_lu     <- dimSums(SoilCarbon[,,c("actualstate")]*Landuse, dim=3)/dimSums(Landuse, dim=3)

SOCStock_natveg[cropland <= 0.001] <- NA
SOCStock_lu[    cropland <= 0.001] <- NA

```

@@

  #LPJmL4
  LPJmL4_CRU <- toolCoord2Isocell(readRDS(paste0("Data/", rev, "histManagement/LPJmL4_CRU.rds")))
  LPJmL4_CRU <- LPJmL4_CRU[,getYears(Landuse),]

  LPJmL4_CRU[cropland            <= 0.001] <- NA
  SoilGrids2[cropland[,"y2010",] <= 0.001] <- NA
  SoilGrids2_full[cropland[,"y2010",] <= 0.001] <- NA

```

@@

  icells <- as.array(climate$cell[climate$IPCC_reduced == climates[i]])
  par(mar = mar[[i]])
  max <- max(    LPJmL4_CRU[icells, years, ], SOCStock_natveg[icells, years, ], na.rm = TRUE)
  min <- c(10, 20, 10, 20)

@@

  points(LPJmL4_CRU[icells ,years ,],SOCStock_natveg[icells, years, ], pch = ".")

@@

  text(min[i], max, paste0("R2=", round(cor(LPJmL4_CRU[icells, years, ],SOCStock_natveg[icells, years, ], 
                                 use = "complete.obs"), 2)), adj = c(0,1))
  text(max, min[i], paste0("Climate zone: ", gsub("_", " ", climates[i])), adj = c(1, 0))
}

@@

print(round(cor(LPJmL4_CRU[, years, ],SOCStock_natveg[, years, ], use = "complete.obs"), 2))

```

@@

climate   <- read.csv("Data/additional/ClimateZoneMapping.csv")
climate$N <- as.integer(substring(climate$cell, 5))
climate   <- climate[order(climate$N),]
climates  <- unique(climate$IPCC_reduced)

@@

  icells <- as.array(climate$cell[climate$IPCC_reduced == climates[i]])
  par(mar = mar[[i]])
  max <- max(    SoilGrids2[icells ,years, ], SOCStock_lu[icells, years, ], na.rm = TRUE)
  min <- c(5, 10, 5, 10)

  plot(SoilGrids2[icells, years, ],SOCStock_lu[icells, years, ], asp = 1, 
       xlab = xlabel[i], ylab = ylabel[i],
       col = "white", pch = ".", log = "xy",
       xlim = c(min[i], max), ylim = c(min[i], max))

  points(SoilGrids2[icells, years, ],SOCStock_lu[icells, years, ], pch = ".")

@@

  text(min[i], max, paste0("R2=", round(cor(SoilGrids2[icells, years, ], SOCStock_lu[icells, years, ], 
                                 use = "complete.obs"), 2)), adj = c(0,1))
  text(max, min[i], paste0("Climate zone: ", gsub("_", " ", climates[i])), adj = c(1, 0))
}

@@

print(round(cor(SoilGrids2[, years, ],SOCStock_lu[, years, ], use = "complete.obs"), 2))

```

@@

InOrOut <- SOCStock_lu[,"y2010",]
InOrOut[] <- NA
InOrOut[SOCStock_lu[,"y2010",] > SoilGrids2_full[,"y2010","SOC_Q05"] & 
        SOCStock_lu[,"y2010",] < SoilGrids2_full[,"y2010","SOC_Q95"]] <- 1
InOrOut[SOCStock_lu[,"y2010",] < SoilGrids2_full[,"y2010","SOC_Q05"]] <- 0.5
InOrOut[SOCStock_lu[,"y2010",] > SoilGrids2_full[,"y2010","SOC_Q95"]] <- 1.5

magpie_coord      <- toolGetMapping("magpie_coord.rda", type="cell")
soilgrid22plot    <- merge(as.data.frame(InOrOut), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")

```

@@

  out <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(data, Year == "2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name     = name,
                      values   = cols,
                      labels   = labels, 
                      na.value = "white",
                      guide    = guide_legend(
                        title.theme    = element_text(size=legend_size),
                        direction      = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust    = 0.5,
                        label.hjust    = 1,
                        nrow           = 1,
                        byrow          = F,
                        label.position = "bottom",
                        keyheight      = 0.5,
                        keywidth       = 2
                      )) +
    theme(legend.position = "bottom",
          axis.title.x     = element_blank(), 
          axis.title.y     = element_blank(),
          legend.text      = element_text(size = legend_size),
          rect             = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7,0.7)),
          plot.margin      = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

cols              <- c("#648FFF", "#DC267F", "#FFB000")[c(1, 3, 2)]
SoilGrids2InMap   <- SOCplotmap( data     =  soilgrid22plot,
                                 limits   = c(0.5, 1.5),
                                 cols     = cols,
                                 name     = expression("Modeled SOC stock in relation to uncertainty range of SoilGrids 2.0"),
                            breaks   = c(0.5, 1.0, 1.5),
                            labels   = c("lower than Q0.05", "inside [Q0.05, Q0.95] ", "higher than Q0.95", "No Cropland"))

SoilGrids2InMap
ggsave(paste0(outputdir, "/SOCquantilesSoilGrids2.png"),    plot=SoilGrids2InMap,    width = 15, height = 10, dpi = 300, units = "cm")

```

>>>>

---
title: "SOC budget analysis in comparsion to LPJmL4 ad SoilGrids 2.0"
output:
  html_document:
    df_print: paged
  pdf_document: default
  bookdown::pdf_document2: default
   keep_md: true
---

@@

SoilCarbon <- readRDS(paste0("Data/", rev, "histManagement/SoilCarbon.rds"))
Landuse    <- readRDS(paste0("Data/", rev, "histManagement/Landuse.rds"))
```

@@

cropland        <- Landuse[, , "crop"]
SOCStock_natveg <- dimSums(SoilCarbon[, , c("naturalstate.natveg")], dim = 3)
SOCStock_lu     <- dimSums(SoilCarbon[, , c("actualstate")] * Landuse, dim = 3) / dimSums(Landuse, dim = 3)

SOCStock_natveg[cropland <= 0.001] <- NA
SOCStock_lu[cropland <= 0.001] <- NA
```

@@

  # LPJmL4
  LPJmL4_CRU <- toolCoord2Isocell(readRDS(paste0("Data/", rev, "histManagement/LPJmL4_CRU.rds")))
  LPJmL4_CRU <- LPJmL4_CRU[, getYears(Landuse), ]

  LPJmL4_CRU[cropland            <= 0.001] <- NA
  SoilGrids2[cropland[, "y2010", ] <= 0.001] <- NA
  SoilGrids2_full[cropland[, "y2010", ] <= 0.001] <- NA
```

@@

  icells <- as.array(climate$cell[climate$IPCC_reduced == climates[i]])
  par(mar = mar[[i]])
  max <- max(LPJmL4_CRU[icells, years, ], SOCStock_natveg[icells, years, ], na.rm = TRUE)
  min <- c(10, 20, 10, 20)

@@

  points(LPJmL4_CRU[icells, years, ], SOCStock_natveg[icells, years, ], pch = ".")

@@

  text(min[i], max, paste0("R2=", round(cor(LPJmL4_CRU[icells, years, ], SOCStock_natveg[icells, years, ],
                                 use = "complete.obs"), 2)), adj = c(0, 1))
  text(max, min[i], paste0("Climate zone: ", gsub("_", " ", climates[i])), adj = c(1, 0))
}

@@

print(round(cor(LPJmL4_CRU[, years, ], SOCStock_natveg[, years, ], use = "complete.obs"), 2))
```

@@

@@

  icells <- as.array(climate$cell[climate$IPCC_reduced == climates[i]])
  par(mar = mar[[i]])
  max <- max(SoilGrids2[icells, years, ], SOCStock_lu[icells, years, ], na.rm = TRUE)
  min <- c(5, 10, 5, 10)

  plot(SoilGrids2[icells, years, ], SOCStock_lu[icells, years, ], asp = 1,
       xlab = xlabel[i], ylab = ylabel[i],
       col = "white", pch = ".", log = "xy",
       xlim = c(min[i], max), ylim = c(min[i], max))

  points(SoilGrids2[icells, years, ], SOCStock_lu[icells, years, ], pch = ".")

@@

  text(min[i], max, paste0("R2=", round(cor(SoilGrids2[icells, years, ], SOCStock_lu[icells, years, ],
                                 use = "complete.obs"), 2)), adj = c(0, 1))
  text(max, min[i], paste0("Climate zone: ", gsub("_", " ", climates[i])), adj = c(1, 0))
}

@@

print(round(cor(SoilGrids2[, years, ], SOCStock_lu[, years, ], use = "complete.obs"), 2))
```

@@

InOrOut <- SOCStock_lu[, "y2010", ]
InOrOut[] <- NA
InOrOut[SOCStock_lu[, "y2010", ] > SoilGrids2_full[, "y2010", "SOC_Q05"] &
        SOCStock_lu[, "y2010", ] < SoilGrids2_full[, "y2010", "SOC_Q95"]] <- 1
InOrOut[SOCStock_lu[, "y2010", ] < SoilGrids2_full[, "y2010", "SOC_Q05"]] <- 0.5
InOrOut[SOCStock_lu[, "y2010", ] > SoilGrids2_full[, "y2010", "SOC_Q95"]] <- 1.5

magpie_coord      <- toolGetMapping("magpie_coord.rda", type = "cell")
soilgrid22plot    <- merge(as.data.frame(InOrOut), data.frame(magpie_coord, Cell = c(1:59199)), by = "Cell")
```

@@

  out <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(data, Year == "2010", c("lon", "lat", "Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name     = name,
                      values   = cols,
                      labels   = labels,
                      na.value = "white",
                      guide    = guide_legend(
                        title.theme    = element_text(size = legend_size),
                        direction      = "horizontal",
                        title.position = "top",
                        # I shift the labels around, the should be placed
                        # exactly at the right end of each legend key
                        title.hjust    = 0.5,
                        label.hjust    = 1,
                        nrow           = 1,
                        byrow          = FALSE,
                        label.position = "bottom",
                        keyheight      = 0.5,
                        keywidth       = 2
                      )) +
    theme(legend.position = "bottom",
          axis.title.x     = element_blank(),
          axis.title.y     = element_blank(),
          legend.text      = element_text(size = legend_size),
          rect             = element_blank(),
          panel.background = element_rect(fill = "#F8F8FF", size = c(0.7, 0.7)),
          plot.margin      = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

@@

cols              <- c("#648FFF", "#DC267F", "#FFB000")[c(1, 3, 2)]
SoilGrids2InMap   <- SOCplotmap(data     =  soilgrid22plot,
                                 limits   = c(0.5, 1.5),
                                 cols     = cols,
                                 name     = expression("Modeled SOC stock in relation to uncertainty range of SoilGrids 2.0"),
                            breaks   = c(0.5, 1.0, 1.5),
                            labels   = c("lower than Q0.05", "inside [Q0.05, Q0.95] ", "higher than Q0.95", "No Cropland"))

SoilGrids2InMap
ggsave(paste0(outputdir, "/SOCquantilesSoilGrids2.png"),    plot = SoilGrids2InMap,    width = 15, height = 10, dpi = 300, units = "cm")
```
